Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
add grants

\ack Figure~\ref{fig:gpu_speedup} was generated using \texttt{Jupyter} \citep{Kluyver2016} and \texttt{matplotlib} \citep{Hunter2007}.

>>>>

\ack Figure~\ref{fig:gpu_speedup} was generated using \texttt{Jupyter}
\citep{Kluyver2016} and \texttt{matplotlib} \citep{Hunter2007}.  The
work at Stony Brook was supported by the SciDAC program DOE grant
DE-SC0017955 and DOE/Office of Nuclear Physics grant
DE-FG02-87ER40317.  The work at LBNL was supported by the DOE Office
of Advanced Scientific Computing Research under Contract No,
DE-AC02-05CH11231.  An award of computer time was provided by the
Innovative and Novel Computational Impact on Theory and Experiment
(INCITE) program. This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No.\ DE-AC05-00OR22725.  This research used
resources of the National Energy Research Scientific Computing Center,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No.\ DE-AC02-05CH11231. This research has made
use of NASA's Astrophysics Data System Bibliographic Services.
